### 2018-12-06 VV556/HW10/submission.tex
done

\title{	
\normalfont \normalsize 
\textsc{Shanghai Jiao Tong University, UM-SJTU JOINT INSTITUTE} \\ [25pt] % Your university, school and/or department name(s)
\horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
\huge Methods of Applied Mathematics I\\ HW9 \\ % The assignment title
\horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
}

@@

\section{Exercise9.1}

@@

						(LKu)(x) & = -\frac{d^2}{d x^2} \int_{0}^{1} g(x, \xi) u(\xi) d\xi\\
								 & = -\frac{d^2}{d x^2} \Bigg(\int_{0}^{x} g(x, \xi) u(\xi) d\xi + \int_{x}^{1} g(x, \xi) u(\xi) d\xi \Bigg)\\
								 & = -\frac{d^2}{d x^2} \Bigg(\int_{0}^{x} \xi(1-x) u(\xi) d\xi + \int_{x}^{1} x(1-\xi) u(\xi) d\xi \Bigg)\\
								 & = -\frac{d^2}{d x^2} \Bigg((1-x)\int_{0}^{x} \xi u(\xi) d\xi + x\int_{x}^{1} (1-\xi) u(\xi) d\xi \Bigg)\\
								 & = -\frac{d}{d x} \Bigg(-\int_{0}^{x} \xi u(\xi) d\xi + \int_{x}^{1} (1-\xi) u(\xi) d\xi \Bigg)\\
								 & = xu(x) + (1-x) u(x) = u(x)

@@

				Thus, $LK=I$, which means $L = K^{-1}$.

@@

				($\Rightarrow$) Suppose $\frac{1}{\lambda}$ is an eigenvalue for $K$, then

@@

					ku = \frac{1}{\lambda}u

@@

					u = \lambda K u

@@

				Take the operator $L$ on it

@@

					Lu = \lambda LKu = \lambda Iu = \lambda u

@@

				which indicates that $\lambda$ is an eigenvalue of $L$.\\
				($\Leftarrow$) Suppose $\lambda \neq 0$ is an eigenvalue of $L$, then

@@

@@

					u = \frac{1}{\lambda} Lu

@@

				As $K = L^{-1}$ is known, take the operator $K$ onto it yields

@@

					Ku = \frac{1}{\lambda}KLu = \frac{1}{\lambda} Iu = \frac{1}{\lambda} u

@@

				which indicates that $\frac{1}{\lambda}$ is an eigenvalue of $K$.\\
				It's clear that for the given $\lambda$, $K$ and $L$ share the same eigenfunction $u(x)$.

@@

				It's obvious that $L$ is bounded over $M$.\\

@@

						<u, Lv> &= -\int_{0}^{1} u(x)v''(x) dx = -\Bigg(u(x)v'(x)\Big|_0^1 - \int_{0}^{1}u'(x)v'(x)dx\Bigg)\\
								&= \int_{0}^{1}u'(x)v'(x)dx = \int_{0}^{1}u'(x)dv(x) = u'(x)v(x)\Big|_0^1 - \int_{0}^{1} v(x)u''(x)dx\\
								& = -\int_{0}^{1} u''(x)v(x)dx = <Lu, v>
				which indicates that $L$ is self-adjoint. Thus the eigenvalues of $L$ are real numbers.\\
		 		The eigenfunction $\psi_n(x)$ of $L$ together with $\lambda_n$ satisfy 
		 			\psi_n''(x) + \lambda_n \psi_n(x) = 0

@@

		 			\psi_n(0) = \psi_n(1) = 0

@@

		 		Solution of this ODE depends on the sign of $\lambda_n$.\\

@@

		 				If $\lambda_n > 0$, then

@@

		 					\psi_n(x) = C_1 sin(\sqrt{\lambda_n}x) + C_2 cos(\sqrt{\lambda_n}x)

@@

		 				apply the boundary condition yields

@@

		 					C_2 = 0

@@

		 					C_1 sin(\sqrt{\lambda_n}) = 0

@@

@@

		 					\lambda_n = (n\pi)^2

@@

		 					\psi_n(x) = C_2 sin(n\pi x) \quad (C_2 \neq 0)
		 				If $\lambda_n = 0$, then
		 					\psi_n(x) = C_0 + C_1 x
		 				Apply the B.C. yields $C_0 = C_1 = 0$, which indicates 0 is not an eigenvalue for $L$.
		 				If $\lambda_n < 0$, then
		 					\psi_n(x) = C_1 e^{\sqrt{-\lambda_n}x} + C_2 e^{-\sqrt{-\lambda_n}x}
		 				Apply the B.C. yields $C_0 = C_1 = 0$, which indicates  $\lambda_n < 0$ are not eigenvalues for $L$.
			It's obvious that, from previous proof, the eigenvalues of $K$ are
				\sigma_{point}(K) = \{\frac{1}{(n\pi)^2}, n=1,2,3, ....\}
			As $K$ is compact and self-adjoint, it's obvious bounded and
				\sigma_{compression}(K) = \sigma_{point}(K)
			If $0$ is an eigenvalue of $K$, then
				Ku = 0
			thus
				LKu = 0 \quad \Rightarrow \quad u = 0
			which indicates that 0 is not an eigenvalue for $K$.\\
			Hence, 
				\sigma_{continous}(K) = {0}
			as $K^{-1} = L$ is unbounded.
			It's obvious that, from previous proof, the eigenfunctions of $K$ are
				u_n(x) = sin(n\pi x) \quad n = 1, 2, ...
			which form the Fouier basis.

>>>>

\title{	
\normalfont \normalsize 
\textsc{Shanghai Jiao Tong University, UM-SJTU JOINT INSTITUTE} \\ [25pt] % Your university, school and/or department name(s)
\horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
\huge Methods of Applied Mathematics I\\ HW10 \\ % The assignment title
\horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
}

@@

\section{Exercise10.1}

@@

						<u, Lu> & = \int_{0}^{1} u(x) u''(x) dx\\
								& = -\Big[uu'\big|_0^1 - \int_{0}^{1}(u'(x))^2 dx\Big]\\
								& =  \int_{0}^{1}(u'(x))^2 dx \geq 0

@@

				Thus, the operator $L$ is positive definite.

@@

				Denote $\lambda$ as the eigenvalue, and $u$ being the corresponding eigenfunction, then

@@

				As has been proved before, the positive definite property of $L$ implies that
					<u, Lu> = <u, \lambda u> = \lambda <u, u> = \lambda ||u||^2 \geq 0

@@

					\lambda > 0

@@

				as the case $\lambda = 0$ is trival.\\
				Then, the solution of this ODE is 

@@

					u(x) = a sin(\sqrt{\lambda} x) + b cos(\sqrt{\lambda} x)

@@

				With the B.C. at endpoints, it follows that

@@

					b = 0
					a(sin(\sqrt{\lambda}) + \sqrt{\lambda}cos(\sqrt{\lambda})) = 0

@@

					sin(\sqrt{\lambda}) + \sqrt{\lambda}cos(\sqrt{\lambda}) = 0

@@

				which indicates that the eigenvalue $\lambda$ satisfies 

@@

					\sqrt{\lambda} = - tan(\sqrt{\lambda})

@@

@@

			From the plot of $y_1(x) = -x$ and $y_2(x) = tan(x)$, the first 2 intersections in $x>0$ region lie in the gap $(\frac{1}{2}\pi, \pi)$ and $(\frac{3}{2}\pi, 2\pi)$.\\
			With the aid of MATLAB, the 2 lowest eigenvalues $\lambda_1$ and $\lambda_2$ are found as

@@

				\lambda_1 = (2.0288)^2 = 4.1160

@@

				\lambda_2 = (4.9132)^2 = 24.1395

@@

@@

			Denote $p(x) = a_0 + a_1 x + a_2 x^2$, the B.V. at endpoints implies that  

@@

				V_1 = \Big\{ p(x) | p(x) =  a_2 (x^2 - \frac{3}{2}x)\Big\}

@@

			Thus, for any $v \in V_1$

@@

					R(v) & = \frac{<v, Lv>}{<v, v>}\\
					     & = \frac{\int_{0}^{1} a_2 (x^2 - \frac{3}{2}x) (-2a_2) dx }{\int_{0}^{1} a_2^2 (x^2 - \frac{3}{2}x)^2 dx}\\
					     & = -2\frac{\int_{0}^{1} (x^2 - \frac{3}{2}x) dx }{\int_{0}^{1} (x^2 - \frac{3}{2}x)^2 dx}\\
					     & = 4.167
			Denote $p(x) = a_0 + a_1 x + a_2 x^2 + a_3 x^3$, the B.V. at endpoints implies that  
				V_2 = \Big\{ p(x) | p(x) =  a_2 (x^2 - \frac{3}{2}x) + a_3 (x^3 - 2x)\Big\}
			Thus, for any $v \in V_2$
					R(v) & = \frac{<v, Lv>}{<v, v>}\\
						& = \frac{\int_{0}^{1} [a_2 (x^2 - \frac{3}{2}x) + a_3(x^2 - 2 x)][2a_2 + 6a_3 x] dx }{\int_{0}^{1} [a_2 (x^2 - \frac{3}{2}x) + a_3(x^2 - 2 x)]^2 dx}\\
						& = \frac{175a_2^2 + 630a_2a_3 + 588a_3^2}{42a_2^2 + 154a_2a_3 + 142a_3^2}
			As the leading coefficient $a_3\neq 0$, then, denote $t \triangleq \frac{a_2}{a_3}$
				R(v) = \frac{175t^2 + 630 t + 588}{42t^2 + 154t + 142}
			It's obvious that $R(v)$ goes to its minimal when $t \rightarrow \infty$, thus $\min R(v) = \frac{175}{42}=4.1667$.
			Firstly, determine the general form of each element $v \in V_3$.\\
			Denote $v(x) = a_2 (x^2 - \frac{3}{2}x) + a_3 (x^3 - 2x)$ as $v \in V_2$, then, as $v$ also lies in $V_1^\perp$, it means
				\int_{0}^{1} (x^2 - \frac{3}{2}x) v(x) dx = 0
			namely
				a_2 \int_{0}^{1} (x^2 - \frac{3}{2}x)^2 dx + a_3 \int_{0}^{1} (x^2 - \frac{3}{2}x)(x^3 - 2x) dx = 0
				a_2 = - \frac{16}{3} a_3
			Hence
				v(x) = a_3(x^3 - \frac{16}{3}x^2 + 6x)

@@

				v''(x) = a_3(6x - \frac{32}{3})

@@

			Thus, for any $v \in V_3$, the second eigenvalue is estimated as

@@

					R(v) & = \frac{<v, Lv>}{<v, v>}\\
						& = -\frac{\int_{0}^{1} (x^3 - \frac{16}{3}x^2 + 6x)(6x - \frac{32}{3}) dx }{\int_{0}^{1} (x^3 - \frac{16}{3}x^2 + 6x)^2 dx}\\
						& = 4.2803

@@
